The language of generalization: Probability, vagueness, and interaction

### 2018-10-08 paper/case1-generics.Rmd
fix rendering

generics.endorsement.insets <- ggplot( gen.inset.distributions.refactored %>%
         mutate(Parameter = factor(Parameter, levels = c("speakerBeliefs", "state_Posterior", "state_Prior"),
                                   labels = c(
                                              "Referent prevalence\n(Endorsement model input)",
                                             "Generic interpretation\n(Interpretation model output)", 
                                             "Prevalence prior\n(Null interpretation)")),
                property = factor(property, levels = c("have spots", "lay eggs", "are female", "carry malaria", "dont eat people"))),
       aes(x = state, y = Parameter, group = Parameter, color = Parameter))+
  scale_y_discrete(expand = c(0.01, 0)) +   # will generally have to set the `expand` option
  scale_x_continuous(expand = c(0, 0), limits = c(0, 1), breaks = c(0, 1))  +    # for both axes to remove unneeded padding
  facet_wrap(~property, nrow = 1)+
  geom_text_repel(data = category.text.labels,
                  aes(label = category, x = x , y = y),
                  inherit.aes = F)+
    #scale_fill_manual(values = c("#636363", "#abdda4", "#2b83ba", "#d7191c"))+
    #scale_color_manual(values = c("#636363", "#abdda4", "#2b83ba", "#d7191c"))+
  ggridges::geom_density_ridges(scale = 1, alpha = 0.3, adjust = 1) +
  scale_fill_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
    scale_color_manual(values = c("#2b83ba", "#636363","#636363"))+
    scale_alpha_manual(values = c(0.6, 0.4, 0))+
    #scale_linetype_manual(values = c(3, 4, 2, 1))+
    scale_linetype_manual(values = c(3, 4, 1))+
    #scale_x_continuous(breaks = c(0, 1), limits= c(0, 1))+
    #scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
    xlab("Prevalence") +
    ylab("")+
    theme(legend.position = "bottom", legend.title = element_blank())+
  guides(color = F)
```

@@

plot_grid(fig.gen.endorse.toprow,
          fig.gen.endorse.priors,
          labels = c("", "C"), nrow = 2, rel_heights = c(1.1, 0.6)
          )
```

>>>>

generics.endorsement.insets <- ggplot( gen.inset.distributions.refactored %>%
         mutate(Parameter = factor(Parameter, levels = c("speakerBeliefs", "state_Posterior", "state_Prior"),
                                   labels = c(
                                              "Referent prevalence\n(Endorsement model input)",
                                             "Generic interpretation\n(Interpretation model output)", 
                                             "Prevalence prior\n(Null interpretation)")),
                property = factor(property, levels = c("have spots", "lay eggs", "are female", "carry malaria", "dont eat people"))),
       aes(x = value, y = Parameter, group = Parameter, color = Parameter))+
  scale_y_discrete(expand = c(0.01, 0)) +   # will generally have to set the `expand` option
  scale_x_continuous(expand = c(0, 0), limits = c(0, 1), breaks = c(0, 1))  +    # for both axes to remove unneeded padding
  facet_wrap(~property, nrow = 1)+
  geom_text_repel(data = category.text.labels,
                  aes(label = category, x = x , y = y),
                  inherit.aes = F)+
    #scale_fill_manual(values = c("#636363", "#abdda4", "#2b83ba", "#d7191c"))+
    #scale_color_manual(values = c("#636363", "#abdda4", "#2b83ba", "#d7191c"))+
  ggridges::geom_density_ridges(scale = 1, alpha = 0.3, adjust = 1) +
  scale_fill_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
    scale_color_manual(values = c("#2b83ba", "#636363","#636363"))+
    scale_alpha_manual(values = c(0.6, 0.4, 0))+
    #scale_linetype_manual(values = c(3, 4, 2, 1))+
    scale_linetype_manual(values = c(3, 4, 1))+
    #scale_x_continuous(breaks = c(0, 1), limits= c(0, 1))+
    #scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
    xlab("Prevalence") +
    ylab("")+
    theme(legend.position = "bottom", legend.title = element_blank())+
  guides(color = F)
```

@@

cowplot::plot_grid(fig.gen.endorse.toprow,
          fig.gen.endorse.priors,
          labels = c("", "C"), nrow = 2, rel_heights = c(1.1, 0.6)
          )
```
